### 2017-03-01 paper/chapters/gan.tex
removed todo
minor changes to GAN part

%%% when introduced, game theory approach
Generative Adversarial Networks (GAN) is a framework proposed in 2014 by Goodfellow et al. \cite{gan:2014} based on a game theoretic approach to generative modeling.
%which has gathered a lot of attention in the deep learning community and in the last few years many extensions have been [proposed] (citations).

@@

Another formulation of the same game is to define the zero-sum game between the generative model and its adversary, the discriminator.
The payoff of the discriminator can be described as the value function $V(G,D)$ while the payoff of the generator is the negative payoff of $D$: $-V(G,D)$.\\
This formulation allows us to define the reached nash equlibium in equation \ref{eq:zerosum_convergence}.
\begin{equation}
  \label{eq:zerosum_convergence}
  G^* = \arg \min_{G} \max_{D} V(G,D)
\end{equation}

@@

\subsection{Stability and Performance}
\label{sub:gan_stability}
In the common case where both function approximators $G$ and $D$ are implemented using deep neural networks, GANs have been shown to be difficult to train using gradient descent.
In fact, there is no guarantee that GANs will converge in the case of using non-convex functions to represent $G$ or $D$.

%These issues have been credited to the problem of finding the nash equilibrium in the minimax-game with continious, high-dimensional parameters instead of more traditional optimization problems.
%TheseAdditionally to these hypothetical thoughts, \cite{gan_distinguish_crit:2014} have shown that these methods may fail to converge.
Acknowledging these problems, Salimans et al.\cite{improved_gan:2016} has studied the stability and performance of GAN in detail, resulting in a number of practical methods improving performance of the training procedure of GANs.
We will take a look at a selection of these methods in the following, focussing on deep neural networks as approximators in both $D$ and $G$.

@@

In order to use convolutional networks in the generator and discriminator, fractionally strided convolutions have been used to basically upsample the image. The exact details of the architecture is beyond the scope of this article, however in addition to the impressive generative performance the authors have shown that the model has learned to produce representional structures in latent space.
Furthermore, as shown in Figure \ref{fig:dcgan_vector} they were able to perform vector artithmetic in the latent space with results indicating that their model was able to arrange the latent space in a useful way.
\todo[inline]{Elaborate on how DCGAN arranges latent space}

>>>>

%%% when introduced, game theory approach
Generative Adversarial Networks (GAN) is a framework proposed in 2014 by Goodfellow et al. \cite{gan:2014} based on a game theoretic approach to generative modeling~\cite[Chapter~20.10.4]{deeplearning:2016}.
%which has gathered a lot of attention in the deep learning community and in the last few years many extensions have been [proposed] (citations).

@@

Another formulation of the same game is to define the zero-sum game between the generative model and its adversary, the discriminator~\cite[Chapter~20.10.4]{deeplearning:2016}.
The payoff of the discriminator can be described as the value function $V(G,D)$ while the payoff of the generator is the negative payoff of $D$: $-V(G,D)$.\\
This formulation allows us to define the reached nash equlibium in equation \ref{eq:zerosum_convergence}.
\begin{equation}
  \label{eq:zerosum_convergence}
  G^* = \arg \min_{G} \max_{D} V(G,D)
\end{equation}

@@

\subsection{Stability and Performance}
\label{sub:gan_stability}
In the common case where both function approximators $G$ and $D$ are implemented using deep neural networks, GANs have been shown to be difficult to train using gradient descent.
In fact, there is no guarantee that GANs will converge in the case of using non-convex functions to represent $G$ or $D$~\cite[p.~700-701]{deeplearning:2016}.

%These issues have been credited to the problem of finding the nash equilibrium in the minimax-game with continious, high-dimensional parameters instead of more traditional optimization problems.
%TheseAdditionally to these hypothetical thoughts, \cite{gan_distinguish_crit:2014} have shown that these methods may fail to converge.

Acknowledging these problems, Salimans et al.\cite{improved_gan:2016} have studied the stability and performance of GAN in detail, resulting in a number of practical methods improving performance of the training procedure of GANs.
We will take a look at a selection of these methods in the following, focussing on deep neural networks as approximators in both $D$ and $G$.

@@

In order to use convolutional networks in the generator and discriminator, fractionally strided convolutions have been used to basically upsample the image. The exact details of the architecture is beyond the scope of this article, however in addition to the impressive generative performance the authors have shown that the model has learned to produce representional structures in latent space.
Furthermore, as shown in Figure \ref{fig:dcgan_vector} they were able to perform vector artithmetic in the latent space with results indicating that their model was able to arrange the latent space in a useful way.
%\todo[inline]{Elaborate on how DCGAN arranges latent space}
